---
title: "Mango Pagedown Test"
author: "Mango The Cat"
date: "`r Sys.Date()`"
output:
  pagedown::html_paged:
    toc: true
    # change to true for a self-contained document, but it'll be a litte slower for Pandoc to render
    self_contained: false
    css:
      - "css/mango-fonts.css"
      - "css/mango-page.css"
      - "css/default.css"
    template: "templates/mango-paged.html"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Chapter Name

## Headings

Our training sections usually start at level 2.


## Fonts

I've managed to change the fonts to Open Sans in `css/mango-fonts.css` that's about it.

### Body

Open Sans

### Titles

Might be OK Open Sans. We used to have level 3 as orange which is easy enough

### Numbering

Currently use `{chapter}`.`{section}`.`{sub-section}`.

Nice to haves would be a chapter front page saying Chapter `{Chapter Number}` `{Chapter Name}`.

### Code

My guess is that the default code is OK but we might want to fancy it up a bit.

```r
# A non-executed R-block

f <- function(x) {
  if (is.null(x)) 0 else x
}
```

where as python code might look like

```python
# python code looks like this
def f(x):
    """Some big long docstring"""
    return(0 if x is null else x)
```

A code block that returns stuff looks like

```{r, runstuff}
f <- function(x) {
  if (is.null(x)) 0 else x
}

f(NULL)
```

I wonder if that code output could be nicer. Not high priority.

## Plots

We do a fair amount of plots with code

```{r, plotwithcode}
library(ggplot2)
ggplot(iris) +
  geom_point(aes(x = Sepal.Width, y = Sepal.Length, colour = Species))
```

We can manually control size but should have nie defaults

We might do plots with suppressed code.

```{r, plotwithoutcode, echo=FALSE}
library(ggplot2)
ggplot(iris) +
  geom_histogram(aes(x = Sepal.Width, fill = Species), bins=20)
```

## Filler 


Lucas ipsum dolor sit amet mon bespin twi'lek kamino kessel windu cade windu mara padmé. Kashyyyk wookiee alderaan twi'lek antilles dooku. Antilles skywalker hutt naboo dantooine mothma. Jabba k-3po twi'lek droid. Mon cade endor jango antilles sidious. Hutt fisto zabrak calrissian mara kenobi endor. Biggs organa darth solo dooku utapau lars. Mothma c-3p0 antilles skywalker yoda moff hutt. Leia antilles jango hutt mon. Wampa watto wicket tatooine tatooine ventress solo. Kenobi thrawn darth mustafar mace moff gonk ben yavin.

Darth mon grievous jinn dagobah luuke. Mon jabba ponda utapau ewok darth skywalker. Mace thrawn lobot vader. Organa qui-gon windu darth tatooine. Lando moff lando jawa qui-gonn ewok mandalore. Darth calamari cade mon dagobah solo. Mon darth secura solo coruscant moff sidious dagobah antilles. Solo solo kessel tatooine ewok wedge fett skywalker utapau. Maul r2-d2 yoda moff kenobi jabba. Palpatine c-3p0 darth darth luuke solo. Darth solo sidious dantooine jabba solo binks mandalore darth. Luke maul kessel dantooine mon solo mandalore solo han.

Tatooine darth jade gonk jabba. Darth dooku organa antilles skywalker lobot ponda luuke kamino. Darth aayla ponda boba jawa darth grievous thrawn. Droid kenobi sidious jawa naboo solo mustafar. Sidious mon moff darth fisto r2-d2. Skywalker antilles dooku calamari solo moff. Tatooine solo skywalker twi'lek. Mara kessel yoda ewok maul. Vader sith k-3po wicket luuke calrissian jade calrissian. Padmé solo darth grievous. Jade solo mon tatooine calamari fisto antilles hutt. Sidious sith skywalker gonk alderaan ben solo jango.

Wedge padmé grievous kit darth dantooine organa. Wedge moff mara moff naboo c-3po kashyyyk. Kessel darth ben dagobah hutt cade antilles. Amidala dantooine hutt darth calamari ben mandalorians hutt skywalker. Watto skywalker owen kamino yavin calrissian twi'lek. Mandalorians wicket kashyyyk yoda jango darth ackbar boba. Skywalker moff skywalker moff. Organa kessel moff lando darth bothan darth. Darth darth amidala droid. Coruscant kashyyyk fisto palpatine jade twi'lek ben. Grievous skywalker padmé windu.
