---
title: "Mango Pagedown Test"
author: "Mango The Cat"
date: "`r Sys.Date()`"
output:
  pagedown::html_paged:
    toc: true
    # change to true for a self-contained document, but it'll be a litte slower for Pandoc to render
    self_contained: false
    css:
      - "css/mango-fonts.css"
      - "css/mango-page.css"
      - "css/default.css"
    template: "templates/mango-paged.html"
    keep_md: true # just for testing
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Chapter Name

## Headings

Our training sections usually start at level 2.


## Fonts

I've managed to change the fonts to Open Sans in `css/mango-fonts.css` that's about it.

### Body

Open Sans

### Titles

Might be OK Open Sans. We used to have level 3 as orange which is easy enough

### Numbering

Currently use `{chapter}`.`{section}`.`{sub-section}`.

Nice to haves would be a chapter front page saying Chapter `{Chapter Number}` `{Chapter Name}`.

### Code

My guess is that the default code is OK but we might want to fancy it up a bit.

```r
# A non-executed R-block

f <- function(x) {
  if (is.null(x)) 0 else x
}
```

where as python code might look like

```python
# python code looks like this
def f(x):
    """Some big long docstring"""
    return(0 if x is null else x)
```

A code block that returns stuff looks like

```{r, runstuff}
f <- function(x) {
  if (is.null(x)) 0 else x
}

f(NULL)
```

I wonder if that code output could be nicer. Not high priority.

## Plots

We do a fair amount of plots with code

```{r, plotwithcode}
library(ggplot2)
ggplot(iris) +
  geom_point(aes(x = Sepal.Width, y = Sepal.Length, colour = Species))
```

We can manually control size but should have nie defaults

We might do plots with suppressed code.

```{r, plotwithoutcode, echo=FALSE}
library(ggplot2)
ggplot(iris) +
  geom_histogram(aes(x = Sepal.Width, fill = Species), bins=20)
```

## Exercises and info boxes

We're going to need some way to make exercise boxes. This could be by applying a class to a section heading: `{.exercise}`

### Exercise {.exercisebox}

It looks like you can use a section header and a class. The code here looks like:

```markdown
### Exercise {.exercisebox}
```

And then this puts everything until the next section heading in a div with the exercise class. This is super easy to style with css. We might want to remove the section label, this is up for discussion.

1. Question 1
2. Question 2

### Warnings

### Watch out! {.warningbox}

Some important warning message. Again, we can remove the section heading with javascript. There is examples of this already in the existing code.

### Info

### Interesting info {.infobox}

When we're done can put icons and style it nicely.

## Filler 

Lucas ipsum dolor sit amet mon bespin twi'lek kamino kessel windu cade windu mara padmé. Kashyyyk wookiee alderaan twi'lek antilles dooku. Antilles skywalker hutt naboo dantooine mothma. Jabba k-3po twi'lek droid. Mon cade endor jango antilles sidious. Hutt fisto zabrak calrissian mara kenobi endor. Biggs organa darth solo dooku utapau lars. Mothma c-3p0 antilles skywalker yoda moff hutt. Leia antilles jango hutt mon. Wampa watto wicket tatooine tatooine ventress solo. Kenobi thrawn darth mustafar mace moff gonk ben yavin.

Darth mon grievous jinn dagobah luuke. Mon jabba ponda utapau ewok darth skywalker. Mace thrawn lobot vader. Organa qui-gon windu darth tatooine. Lando moff lando jawa qui-gonn ewok mandalore. Darth calamari cade mon dagobah solo. Mon darth secura solo coruscant moff sidious dagobah antilles. Solo solo kessel tatooine ewok wedge fett skywalker utapau. Maul r2-d2 yoda moff kenobi jabba. Palpatine c-3p0 darth darth luuke solo. Darth solo sidious dantooine jabba solo binks mandalore darth. Luke maul kessel dantooine mon solo mandalore solo han.
